Several studies both on user profiling and on real-time automatic trip
itinerary generation have been carried out throughout the years. 

There are many types of systems which help the travellers in their
trips. Gavalas et al. \cite{Gavalas2014} categorised these into
\textbf{POI recommenders, Tourist Service Recommenders, Collaborative
content from users and social media services, path recommenders} and
\textbf{Personlised multiple-day tour planners}. The planning of a
trip to a traveller introduces the Tourist Trip Design Problem (TTDP)
which has recieved a lot of observation and heuristic contribution
\cite{Gunawan2016,Delic2018}. Sylejmani et al.\cite{Sylejmani2017}
have defined the TTDP as part of the Orienteering Problem(OP). OP
problems contain a number of nodes each containing a score and try to
solve the path containing the maximal score constrained with
parameters such as time and budget \cite{Gunawan2016}. There are many
solutions to this problem which will be discussed in the next section.
% Maybe talk about OP..etc

\subsection{Tourist Recommender Systems}

    In 2004, a paper by Dunstall et al. \cite{DUNSTALL2008a} was
    published using a prototype called the The Electronic Travel
    Planner (ETP). This system selects destinations by determining
    activities based on the user’s preferences. Each activity is
    stored in a relational database with information such as duration,
    availability, date and time categorised as either tours, lodging
    or transportation. The requirements for forming such an itinerary
    include the number of children and adults, the location, the date
    range, budget and user preferences in the form of \emph{mandatory,
    at least once, desired, forbidden and permitted} activities. Since
    examples given in the paper took 15-45 seconds to process the
    resulting running time was listed as an issue.

    The Recommender System (RS) was provided by Sebatsia et al.
    \cite{Sebastia2009a} and Garcia et al. \cite{Garcia2011} to
    suggest tourist locations. User preferences are collected in the
    form of age, gender, nationality and ontology. The recommender is
    based on 5 techniques, \emph{Demographic recommendation,
    collaborative recommendation, content based recommendation and
    knowledge based recommendation}. 

    A different approach using social media was presented by Choudhury
    et al. \cite{DeChoudhury2010} in 2010 and Brilhante et al.
    \cite{RamalhoBrilhante2014}. Geo-referenced Flickr
    \footnote{\url{https://www.flickr.com/}} content alongside
    Wikipedia \footnote{\url{https://www.wikipedia.org/}} information
    was used to gather information such as the date, location and
    popularity of the photos being uploaded. An OP algorithm was then
    used to generate the ideal number of Point of Interests (POI).

    A tabu Search approach was proposed by Sylejmani et al.
    \cite{Sylejmani2012} as a Multi Constrained Team Orienteering
    Problem with Time Windows (\textbf{MCTOPTW}), an advanced form of
    the OP.In this algorithm, three steps were used in order to
    generate the activity plan. A new activity is added as a node to
    the trip using \emph{Insert}, A node is exchanged with a new
    activity using \emph{Replace} and two nodes are swapped using
    \emph{Swap}. A pair of tabu lists structured frequently are used
    to avoid repeating solutions.


    Recently, a solution towards presenting an itinerary solving
    conflicts between multiple tourists with different preferences was
    proposed by  \cite{Sylejmani2017}. All tourists are split into
    groups by preference, during certain activities the itinerary
    splits up the groups to visit their specific POI. Before the trip
    one of the options is selected: 
    \begin{enumerate}
        \item \textbf{Solo}: A trip for a single person.
        \item \textbf{Subgroups}: The tourists are separated into
        smaller groups by preference and travel together.
        \item \textbf{All Together}: One itinerary for all Tourists.
        \item \textbf{Tourists Combined}: At certain times, tourists
    are separated to meet their personal preferences

    \end{enumerate}





\subsection{User Profiling for Travel Preferences}
 